\documentclass{article}
\usepackage[german]{babel}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{graphicx}
\lhead{Computational Methods for Document Analysisc 02}
\rhead{Mirco Dietrich\\ Maurice-Roman Isele}
\pagestyle{fancy}
\title{Computational Methods for Document Analysis 02}
\author{Mirco Dietrich\\ Maurice-Roman Isele}

\begin{document}
\maketitle
\section*{Exercise 2}
Problem 1:\\
People don't always use a white-space after a punctuation mark or use multiple marks. Replacing each punctuation mark by an empty string will glue the last and first word of sentences together.
So we needed to replace each punctuation mark by a whitespace and then reduce multiple whitespaces to one.\\
\\
Problem 2:\\
' Should be removed around words if it is used as a quotation mark, but shouldn't be removed when it is used as a abbreviation.
Since there are not that many quotes with "'" we decided to not remove "'".
There would be a solution although it would be a bit of a hack.
You could read in a file with the tokens, replace "'," , "[" , "]" , "," , " '" with whitespaces, split at whitespaces and save the new tokens in the Review object.\\
\\
Problem 3:\\
Removing ",","." and "/" splits numbers separated by them(e.g. decimals, fractions). We don't have a solution for that.


\section*{Exercise 3}

One of the obvious problems was to identify the abbreviations used by the people reviewing. We solved this by looking at the data and furthermore considering more common abbreviations used in the English language. Additionally, any name abbreviations are possible, e.g. \textit{''Mr. K.''}, \textit{''T.J.''}, and so on. \\

A more complex problem was to decide whether an abbreviation is the end of the sentence or not. For example, in \textit{''[...] mental insanity, suicide, etc. However, if you don't want [...]''} the abbreviation is the end of a sentence, but in \textit{[...] acting, storyline, etc. of this were good [...]} it is not. You can't decide this by only considering punctuation and a list of all abbreviations. You could say that an upper-case letter helps you identify the beginning of the next sentence in this scenario, but you have to consider 1) you always write names in upper-case (like New York) and 2) you can't count on the user to use correct spelling and grammar. That's why we never use dots in abbreviations to split the string. \\

The last problem was dealing with multiple dots/question marks/exclamation marks, and again deciding whether the sentence ended after multiple dots, which leads to the same problem. With our current knowledge in text analysis (no grammar etc.), this seems to be the best we can do.

\section*{Exercise 4}

\end{document}
